MCC Preference Kids

### 2019-02-24 papers/cogsci2019/cogsci2019.Rmd
kids model prediction with replication data

output: cogsci2016::cogsci_paper
#final-submission: \cogscifinalcopy
---

@@

<!-- \vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}} \vspace{1em} -->

@@

<!-- MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229. -->

>>>>

output: cogsci2016::cogsci_paper
final-submission: \cogscifinalcopy
---

@@

\vspace{1em} \fbox{\parbox[b][][c]{7.3cm}{\centering Corresponding data and code are available at\ \url{https://github.com/manuelbohn/mcc}}} \vspace{1em} -->

@@

MB received funding from the European Union’s Horizon 2020 research and innovation programme under the Marie Sklodowska-Curie grant agreement No 749229.

### 2019-02-24 stats/kids/kids_inf_biling.Rmd
kids model prediction with replication data

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_data_2/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,47,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

length(unique(raw_data$subid))

d_raw <-raw_data %>%
  mutate(test_date = as.Date(test_date),
         experiment = "mcc_kids_inf_2_2",
         subid= ifelse(subid=="193101_1_inf2","190131_1_inf2",subid))

log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "inf2")%>%
  select(subid,experimenter,keep_drop,sex,dob)

length(unique(log$subid))

sum(log$keep_drop=="drop")

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))

length(unique(d$subid))

#write_csv(d, "../data/kids_inf_2_data.csv")

@@

d %>%
  group_by(subage)%>%
  summarise(n = length(unique(subid)))%>%
  knitr::kable(digits = 2)

@@

# Plot filler by age

```{r filler by age, echo= FALSE, warning= FALSE}
pf1 <- d %>%
      filter(trial == "filler1" | trial == "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

pf2 <- pf1 %>%
  multi_boot_standard(col = "correct")

ggplot() +
  geom_jitter(data = pf1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = pf2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

@@

p1 <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(control,subage, subid) %>%
  summarise(correct = mean(correct))

@@

ggplot() +
  geom_jitter(data = p1, aes(x = control, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = control, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Control",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

@@

```{r plot by numerical age, echo = F}
p5 <- d %>%
  filter(trial != "filler1",
         trial != "filler2") %>%
  group_by(age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_smooth(method = "lm", se = T)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized(name="Speaker Change",
                     breaks=c("false", "true"),
                     labels=c("No", "Yes"))
```

>>>>

raw_data_2 <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_data_2/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,47,str_length(jf)-11)
  id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
  raw_data_2 <- bind_rows(raw_data_2, id)
}

d_raw_2 <-raw_data_2 %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  mutate(test_date = as.Date(test_date),
         experiment = "mcc_kids_inf_2_2",
         subid= ifelse(subid=="193101_1_inf2","190131_1_inf2",subid))%>%
  select(subid,subage,trial,correct,test_date)

files <- dir("~/Work/MCC/git-mcc/kids_info_data/")

d_raw <-raw_data %>%
    filter(trial != "filler1",
         trial != "filler2")%>%
  mutate(test_date= ifelse(test_date == "18-10-10", paste(20,test_date,sep = ""),test_date),
         subid= ifelse(subid == "101018_8_inf", "181010_8_inf",subid),
         subid= ifelse(subid == "181031_3", "181031_3_inf",subid),
         test_date= ifelse(test_date == "18-XX-XX", "2018-10-10",test_date),
         test_date= ifelse(test_date == "18-09-12", "2018-09-12",test_date),
         experiment = "mcc_kids_inf_2")%>%
  select(subid,subage,trial,correct,test_date)%>%
  mutate(test_date = as.Date(test_date))

files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/trees")

raw_data_trees <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/trees/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,50,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data_trees <- bind_rows(raw_data_trees, id)
}

d_trees <- raw_data_trees %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "filler1",
         trial != "filler2",
         subage != "Test")%>%
  mutate(test_date = as.Date(test_date))%>%
  select(subid,subage,trial,correct,test_date)

files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_4_map")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/robots_point_4_map/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,63,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

d_robots <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "filler1",
         trial != "filler2",
         subage != "Test")%>%
  mutate(test_date = as.Date(test_date))%>%
  select(subid,subage,trial,correct,test_date)

files <- dir("~/Work/MCC/git-mcc/kids_info_pilot/trees_left_right")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("~/Work/MCC/git-mcc/kids_info_pilot/trees_left_right/",f,sep="")
  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
  date <- str_sub(jf,61,str_length(jf)-11)
  id <- as_data_frame(jd$data$data)%>% mutate(test_date = date)
  raw_data <- bind_rows(raw_data, id)
}

d_trees_left_right <- raw_data %>%
  filter(trial != "train1",
         trial != "train2",
         trial != "filler1",
         trial != "filler2",
         subage != "Test")%>%
  mutate(test_date = as.Date(test_date))%>%
  select(subid,subage,trial,correct,test_date)

d_sum <- bind_rows(
  d_raw_2,
  d_raw,
  d_trees,
  d_robots,
  d_trees_left_right)

log <- read_excel("../../../MCC-subject_log.xlsx", 1)%>%
  filter(Condition == "inf" | Condition == "inf2")%>%
  select(subid,experimenter,keep_drop,sex,dob, English, parent1_ed,parent2_ed)%>%
  mutate(language_status = ifelse(English == "100" | English == "90-95", "mono_ling", "bi_ling"))

d <- left_join(d_sum,log, by = "subid")%>%
  mutate(dob = as.numeric(dob),
         dob = as.Date(dob,origin = "1899-12-30"),
         age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
  filter(language_status != "NA", 
         English != "NA")

write_csv(d, "../data/kids_inf_data_megan.csv")

@@

d %>%
  group_by(subage, sex)%>%
  summarise(n = length(unique(subid)))

@@

@@

p1 <- d %>%
  group_by(sex,subage, subid) %>%
  summarise(correct = mean(correct))

@@

ggplot() +
  geom_jitter(data = p1, aes(x = sex, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p2, aes(x = sex, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_wrap(~subage)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_colour_solarized()
```

@@

```{r plot by numerical age, echo = F}
p5 <- d %>%
  group_by(language_status,age_num, subid) %>%
  summarise(correct = mean(correct))

ggplot(data = p5, aes(x = age_num, y = correct,col = language_status)) +
  geom_smooth(method = "lm", se = T)+
  geom_jitter( alpha = .5, height = 0.04)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  #theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  scale_colour_solarized()
```

### 2019-02-24 stats/kids/kids_model_predictions.Rmd
kids model prediction with replication data

## Model parameters by age bin

@@

## Basic RSA model predictions

@@

## Noisy model predictions

```{r}
ageConditions <- data.frame(
  age_bin = rep(seq.int(0, 1.95, 0.05),4),
  Speaker = c(rep("same_speaker",80),rep("different_speaker",80)),
  Alignment = c(rep("congruent",40),rep("incongruent",40),rep("congruent",40),rep("incongruent",40)))
```

var ex3Data = dataFromR.ex3data
var modelParams = dataFromR.modelParams[0]
var ageConditions = dataFromR.ageConditions

@@

@@

   var ageSpecificParams =  _.filter(modelParams, {age_bin: conditionInfo.age_bin})

    display(JSON.stringify(ageSpecificParams))

    var speakerOptimality = ageSpecificParams.so_map

    var diff_priorReg = ageSpecificParams.diff_priorReg_map

    map(function(d){ 
      observe(noisyRsaPredictions_diff_cong, d.correct_inf)
    }, ageConditionSpecificData)

  return  [conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment, Math.exp(noisyRsaPredictions_diff_cong.score(1))]

}, ageConditions)

```{r}
noisy_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
  data =list(ex3data = ex3_data, modelParams = model_params_by_age, ageConditions = ageConditions),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 10, burn = 2, verbose = T)
)

@@

## Prior only model

@@

## Plot comparing model and data by continous age
```{r comparison plot by age, echo= FALSE}

@@

ggplot(kids_model_pred)+
  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
  #geom_ribbon(aes(x =age_bin, ymin = lci, ymax = uci, fill = model), alpha = .4) +
  geom_line(aes(age_bin, prop_informative, col = model), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
  #geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
  ylim(-0.05,1.05)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()

@@

data <- d %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(Speaker, Alignment ,subage) %>%
  summarize(k = sum(correct_inf), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         Data_ci_lower  = qbeta(.025, a, b),
         Data_ci_upper = qbeta(.975, a, b),
         Data = (a-1)/(a+b-2))%>%
  select(-a,-b,-n,-k)

model <- model_comp %>%
  mutate(subage = ifelse(age_bin<1,"3","4"))%>%
  group_by(model,Speaker,Alignment,subage)%>%
  summarise(Model = mean(prop_informative),
            Model_ci_lower = hdi_lower(prop_informative),
            Model_ci_upper = hdi_upper(prop_informative))

cor_plot <- model %>%
  ungroup()%>%
  mutate(Data = rep(data$Data,3),
         Data_ci_lower = rep(data$Data_ci_lower,3),
         Data_ci_upper  =rep(data$Data_ci_upper,3))

ggplot(data = cor_plot,aes(x = Model, y = Data, col = subage)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
  geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
  coord_fixed()+
  stat_cor(method = "pearson", label.x = 0.1, label.y = 0.9, aes(x = Model, y = Data), inherit.aes = F)+
  facet_grid(~model)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few(base_size = 10) + 
  scale_colour_solarized()

>>>>

## Across age bins

### RSA model predictions across age bins

```{r}
modelPredAcrossWebppl <- '
var levels = function(df, label){
  return _.uniq(_.map(df, label));
}
var prefData = _.filter(dataFromR, {experiment: "preference_pretest"})
var infData = _.filter(dataFromR, {experiment: "informativeness_pretest"})
// make finer grained as needed
var binned_age_range = _.range(0, 2, 0.05)
var all_conditions = levels(prefData, "condition")
var foreach = function(fn, lst) {
    var foreach_ = function(i) {
        if (i < lst.length) {
            fn(lst[i]);
            foreach_(i + 1);
        }
    };
    foreach_(0);
};
var logistic = function(x) {1 / (1 + Math.exp(-x))}
var model  = function(){
  var so_slope = uniformDrift({a: -2, b: 2, width: 0.4})
  var so_int = uniformDrift({a: -2, b: 2, width: 0.4})
  foreach(function(row){
    var age = row.age_num
    var speakerOptimality = so_int  + so_slope * (age - infData[0].minage)

    var diff_priorReg = logistic(diff_speaker_params.pref_int +
            diff_speaker_params.pref_slope * age_bin)
    var diff_priorProbs_congruent = [1-diff_priorReg, 1-diff_priorReg, diff_priorReg]
    var diff_priorProbs_incongruent = [diff_priorReg, diff_priorReg, 1-diff_priorReg]

    var rsaPredictions_diff_cong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_congruent,   speakerOptimality))
    var rsaPredictions_diff_incong = expectation(pragmaticListener({label: "dax", point: 2 }, diff_priorProbs_incongruent, speakerOptimality))

    var same_priorReg = logistic(same_speaker_params.pref_int +
            same_speaker_params.pref_slope * age_bin)
    var same_priorProbs_congruent = [1-same_priorReg, 1-same_priorReg, same_priorReg]
    var same_priorProbs_incongruent = [same_priorReg, same_priorReg, 1-same_priorReg]
    var rsaPredictions_same_cong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_congruent, speakerOptimality))
    var rsaPredictions_same_incong = expectation(pragmaticListener({label: "dax", point: 2 }, same_priorProbs_incongruent, speakerOptimality))
    return extend(
    // diff_speaker_params, same_speaker_params, 
      {
     diff_priorReg,
     same_priorReg,
     speakerOptimality,
    rsaPredictions_diff_cong,
    rsaPredictions_diff_incong,
    rsaPredictions_same_cong,
      rsaPredictions_same_incong,
      age_bin,
    //  so_slope,
    //  so_int,
    })

Taking samples and munging the data.

```{r combined model predictions}
model_pred_across <- readRDS("../saves/kids_model_predictions.rds")

model_pred_across<- webppl(
  program_code = paste(rsaUtils, rsaModel, modelPredAcrossWebppl , sep='\n'),
  data = pre_data,
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 900, burn = 200, verbose = T)
)

saveRDS(model_pred, file = "../saves/kids_model_predictions.rds")

kids_model_pred_across <- model_pred_across%>%
  select(value) %>%
  map_df(bind_rows)%>%
  mutate(iteration = rep(1:3600,each = 40))%>%
  select(-diff_priorReg,-same_priorReg,-speakerOptimality,-so_slope,-so_int)%>%
  gather(condition, prop_informative, -iteration,-age_bin)%>%
  separate(condition, into = c("model", "Speaker", "Alignment"), sep="_")%>%
  mutate(Speaker = ifelse(Speaker == "diff", "different_speaker","same_speaker"),
         Alignment = ifelse(Alignment == "cong", "congruent","incongruent"))

kids_model_pred_so <- model_pred%>%
  select(value) %>%
  map_df(bind_rows)%>%
  mutate(iteration = rep(1:3600,each = 40))%>%
  select(so_slope,so_int,age_bin,iteration,speakerOptimality)

kids_model_pred_prior <- model_pred%>%
  select(value) %>%
  map_df(bind_rows)%>%
  mutate(iteration = rep(1:3600,each = 40))%>%
  select(age_bin,iteration,diff_priorReg,same_priorReg)%>%
  gather(condition, prop_preferred, -iteration,-age_bin)%>%
  mutate(condition = ifelse(condition == "diff_priorReg", "different_speaker","same_speaker"))

## By age bin with noise

### Model parameters by age bin

@@

### RSA model predictions by age bin

@@

### Noisy RSA predictions by age bin

```{r}
ageConditions <- data.frame(
  age_bin = rep(seq.int(0, 1.95, 0.05),4),
  Speaker = c(rep("same_speaker",80),rep("different_speaker",80)),
  Alignment = c(rep("congruent",40),rep("incongruent",40),rep("congruent",40),rep("incongruent",40)))

ageParams <- data.frame(
  age_bin = rep(seq.int(0, 1.95, 0.05),4),
  Speaker = c(rep("same_speaker",80),rep("different_speaker",80)),
  Alignment = c(rep("congruent",40),rep("incongruent",40),rep("congruent",40),rep("incongruent",40)),
  SpeakOpt = rep(model_params_by_age$so_map,4))

listPrior <- data.frame(
  a = 1:length(ageParams$age_bin),
  ob1 = c(1- model_params_by_age$same_priorReg_map,
          model_params_by_age$same_priorReg_map,
          1- model_params_by_age$diff_priorReg_map,
          model_params_by_age$diff_priorReg_map),
  ob2 = c(1- model_params_by_age$same_priorReg_map,
          model_params_by_age$same_priorReg_map,
          1- model_params_by_age$diff_priorReg_map,
          model_params_by_age$diff_priorReg_map),
  ob3 = c(model_params_by_age$same_priorReg_map,
          1- model_params_by_age$same_priorReg_map,
          model_params_by_age$diff_priorReg_map,
          1- model_params_by_age$diff_priorReg_map))%>%
  group_by(a)%>%
  mutate(list = list(c(ob1,ob2,ob3)))%>%
  pull(list)

ageParams$priorP <- listPrior

```{r}
noisyModelPredWebppl <-'
var allConditions = dataFromR.ageConditions
var allData = dataFromR.ex3data
var allParams = dataFromR.ageParams

@@

  var conditionSpecificData =  _.filter(allData, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})

      var ageConditionSpecificParams =  _.filter(allParams, {age_bin: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})

    //display(JSON.stringify(ageConditionSpecificParams[0].priorProbs))

   var modelPredictions = pragmaticListener({label: "dax", point: 2 }, ageConditionSpecificParams[0].priorProbs,   ageConditionSpecificParams[0].SpeakOpt)

   var noisyModelPredictions = addNoise(modelPredictions, noise)

   map(function(d){ 
     // display(JSON.stringify(noisyModelPredictions) + JSON.stringify(d.correct_inf))
      observe(noisyModelPredictions, d.correct_inf)
    }, conditionSpecificData)

  return  [conditionInfo.age_bin + "-" + conditionInfo.Speaker + "-" +  conditionInfo.Alignment, Math.exp(noisyModelPredictions.score(1))]

}, allConditions)

 return extend(_.fromPairs(conditionOutput), {noise: noise})
}
'
```

```{r}
noisyModelPredWebppl <- '
var levels = function(df, label){
  return _.uniq(_.map(df, label));
}

var ex3Data = dataFromR.ex3data
var ageConditions = dataFromR.ageConditions
var ageParams = dataFromR.ageParams

display(JSON.stringify(ageParams))

var model = function(){
  var noise = uniformDrift({a: 0, b:1, width: 0.1})
 // var predict_by_age = function(age_bin){

@@

   var ageConditionSpecificParams =  _.filter(ageParams, {binned_age: conditionInfo.age_bin, Speaker: conditionInfo.Speaker, Alignment: conditionInfo.Alignment})

 display(JSON.stringify(ageConditionSpecificParams))

    var rsaPredictions = pragmaticListener({label: "dax", point: 2 }, ageConditionSpecificParams[0].Prior,   ageConditionSpecificParams[0].SpeakOpt)

    var noisyRsaPredictions_diff_cong = addNoise(rsaPredictions_diff_cong, noise)
    map(function(d){ 
    observe(noisyRsaPredictions_diff_cong, d.correct_inf)
    }, ageConditionSpecificData)
  // display(conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment)
  // display(Math.exp(noisyRsaPredictions_diff_cong.score(1)))

  return  [conditionInfo.age_bin + "_" + conditionInfo.Speaker + "_" +  conditionInfo.Alignment, Math.exp(noisyRsaPredictions_diff_cong.score(1))]
  }, ageConditions)
//  }
//  var predictions_by_age = map(predict_by_age, modelParams)
  //display(JSON.stringify(predictions_by_age))
//  return predictions_by_age
}
'
```

```{r}
noisy_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, noisyModelPredWebppl , sep='\n'),
  data =list(ex3data = ex3_data %>% mutate(binned_age = as.numeric(as.character(binned_age))), 
             ageConditions = ageConditions,
             ageParams = ageParams),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "MCMC", samples = 1000, burn = 200, verbose = T)
)

posterior.noise <- noisy_model_pred %>%
  filter(Parameter %in% c("noise", "priorExponent"))

ggplot(posterior.noise, aes(x = value))+
  geom_histogram()+
  facet_wrap(~Parameter, scales = 'free')

posterior.predictive <- noisy_model_pred %>%
  filter(!(Parameter %in% c("noise", "priorExponent"))) %>%
  separate(Parameter, into = c("age_bin", "Speaker", "Alignment"), sep="-")%>%
  group_by(age_bin,Alignment,Speaker) %>%
  summarise(mean = estimate_mode(value), 
            ci_lower = hdi_lower(value), 
            ci_upper =hdi_upper(value))%>%
  ungroup()%>%
  mutate(age_bin = as.numeric(age_bin))

@@

### Prior only model

@@

## Predictions across age bins

```{r comparison plot, echo= FALSE}

@@

ggplot(posterior.predictive)+
  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x =age_bin, ymin = ci_lower, ymax = ci_upper), alpha = .4) +
  geom_line(aes(age_bin, mean), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
  ylim(-0.05,1.05)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()

## Predictions by age bin

### Plot comparing noisy model and data by continous age
```{r comparison plot by age, echo= FALSE}

ggplot(posterior.predictive)+
  #geom_jitter(data = p_data, aes(x = age_bin, y = correct_inf), width = .025,height = .025, alpha = .2)+
  geom_ribbon(aes(x =age_bin, ymin = ci_lower, ymax = ci_upper), alpha = .4) +
  geom_line(aes(age_bin, mean), size = 1, alpha = 1, linetype = 1) + 
  geom_smooth(data = p_data, aes(x = age_bin, y = correct_inf), col = "black", size = 0.6, method = "glm", method.args = list(family = "binomial"),  se = T,  alpha = .5, size = .4)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(y="proportion more informative")+
  scale_x_continuous(limits=c(0,2), name="age", breaks = c(0,0.5,1,1.5,2), labels = c(3.0,3.5,4.0,4.5,5)) +
  ylim(-0.05,1.05)+
  facet_grid(Speaker~Alignment)+
  theme_few()+
  scale_color_solarized()+
  scale_fill_solarized()

@@

data <- ex3_data %>%
  filter(trial != "filler1",
         trial != "filler2")%>%
  group_by(Speaker, Alignment ,subage) %>%
  summarize(k = sum(correct_inf), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         Data_ci_lower  = qbeta(.025, a, b),
         Data_ci_upper = qbeta(.975, a, b),
         Data = (a-1)/(a+b-2))%>%
  select(-a,-b,-n,-k)

model <- kids_model_pred %>%
  mutate(subage = ifelse(age_bin<1,"3","4"))%>%
  group_by(model,Speaker,Alignment,subage)%>%
  summarise(Model = mean(prop_informative))

cor_plot <- model %>%
  ungroup()%>%
  mutate(Data = data$Data,
         Data_ci_lower = data$Data_ci_lower,
         Data_ci_upper  =data$Data_ci_upper,3)

ggplot(data = cor_plot,aes(x = Model, y = Data, col = subage)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_point(size = 3)+
  geom_errorbar(aes(ymin = Data_ci_lower, ymax = Data_ci_upper),width = 0,size = .5)+
  #geom_errorbarh(aes(xmin = Model_ci_lower, xmax = Model_ci_upper), height = 0,size = .5)+
  coord_fixed()+
  stat_cor(method = "pearson", label.x = 0.1, label.y = 0.9, aes(x = Model, y = Data), inherit.aes = F)+
  facet_grid(~model)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  theme_few(base_size = 10) + 
  scale_colour_solarized()

### 2019-02-24 stats/kids/kids_pref.Rmd
kids model prediction with replication data

d <- read_csv(file="data/kids_pref_data.csv")

@@

lm_data <- d%>%
  filter(trial_type == "test")%>%
  mutate(choiceAgent = ifelse( change == "false", agent, altAgent),
         age_num = scale(age_num, center = TRUE, scale = TRUE))

>>>>

d <- read_csv(file="../data/kids_pref_data.csv")

@@

lm_data <- d%>%
  filter(trial_type == "test")%>%
  mutate(choiceAgent = ifelse( change == F, agent, altAgent),
         age_num = scale(age_num, center = TRUE, scale = TRUE))
